The Practical Application of Computerised Multistage Tests

### 2021-03-05 article.Rmd
Finalised article

---
title: "The Practical Application of Computerised Multistage Tests"
description: A practical guide to the design and development of computerised multistage
  tests.
author:
- name: James Page
  affiliation: SP Educational Consulting
  affiliation_url: https://www.speduconsulting.co.uk/
date: "`r Sys.Date()`"
version: 1
output:
  pdf_document: 
    highlight: tango
    latex_engine: xelatex
    toc: yes
    toc_depth: 2
    fig_caption: yes
    fig_width: 5
    fig_height: 4
  html_document:
    df_print: paged
    toc: true
    toc_depth: 2
    fig_caption: true
  word_document:
    toc: true
    toc_depth: 2
    fig_caption: true
bibliography: references.bib
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(janitor)

@@

```{r show simulated test, echo=FALSE, fig.cap="Example module routing"}
plot(dfMSTResponse)
```

@@

```{r test-design-params, echo=FALSE}
designParams <- read_csv('mst-designs.csv', skip = 1) %>%
  clean_names() %>%
  dplyr::select(-total)

knitr::kable(
  designParams, booktabs = TRUE,
  caption = 'MST Design paramaters (modules sizes and mean difficulties).'
)
```

@@

To run the simulations we'll create a set of simulated candidates with an ability range between -4 and 4 (stepped in increments of 0.5). Then we'll repeat for each of the six designs above, with the same item bank.

@@

```{r}
knitr::kable(
  head(designParams, n = 1), booktabs = TRUE,
  caption = 'MST Design 1'
)
```

@@

knitr::kable(
  head(dfTestResponses[1:8]), booktabs = TRUE,
  caption = 'Example Test Reponses'
)
```

@@

knitr::kable(
  head(dfCronbachsAlpha), booktabs = TRUE,
  caption = "Cronbach's Alpha"
)

ggplot(dfCronbachsAlpha, 
       aes(x=alpha, y=num_responses, size = num_items, color = moduleNames)) +
    geom_point() +
    scale_x_continuous(limits = c(0, 1)) +
    theme(legend.position = "right") +
    labs(x = "alpha", y = "# responses") +
    geom_vline(xintercept = 0.7, linetype="dotted")
```
Ideally, we're looking for alphas of 0.7 and above; less than this indicates that there is weak covariance between the items in the module, which means they may not be testing the same trait. This measure is really only useful as a guide for further investigations; the ultimate decision on whether to modify the items in each module should be taken in collaboration with the subject matter experts.

@@

This chart makes it easy to spot any outlier items have a very large divergence from the mean; it is best to remove these items from the item bank as they have too large an error to be used in a live test. Usually this is the result of them having all 1's or 0's (in other words they are too easy or too difficult for all candidates who took them).

@@

```{r Stage 1 MCC}
moduleA1_items <- which(colnames(dfTrial) %in% colnames(dfModuleAItems))
plotData <- trueScoreSummary(plot(raschmodel, 
                                  type = "ICC", 
                                  items = moduleA1_items, plot = FALSE), 
                             "A")
ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line() +
  labs(title="Module Characteristic Curve", x="theta", y="True Score")
```

@@

ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="theta", y="True Score")
```

@@

ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="theta", y="True Score")
```

>>>>

---
title: "The Practical Application of Computerised Multistage Tests"
description: A practical guide to the design and development of computerised multistage
  tests.
author:
- name: James Page
  affiliation: SP Educational Consulting
  affiliation_url: https://www.speduconsulting.co.uk/
date: "`r Sys.Date()`"
version: 1
output:
  pdf_document: 
    highlight: tango
    latex_engine: lualatex
    toc: yes
    toc_depth: 2
    fig_caption: yes
    fig_width: 5
    fig_height: 4
  html_document:
    df_print: paged
    toc: true
    toc_depth: 2
    fig_caption: true
  word_document:
    toc: true
    toc_depth: 2
    fig_caption: true
bibliography: references.bib
---

```{r setup, include=FALSE}
library(kableExtra)
library(tidyverse)
library(janitor)

@@

```{r show simulated test, echo=FALSE, fig.cap="Example routing", message=FALSE}
plot(dfMSTResponse)
```

@@

```{r test-design-params, echo=FALSE, message=FALSE}
designParams <- read_csv('mst-designs.csv', skip = 1) %>%
  clean_names() %>%
  dplyr::select(-total)

displayParams <- designParams %>%
  rename(Design=design, `1`=stage1, `2`=stage2, `3`=stage3,
         A=module_a, B=module_b, C=module_c,
         D=module_d, E=module_e, F=module_f, G=module_g)

kbl(displayParams, caption = 'MST design paramaters')  %>%
  kable_styling() %>%
  add_header_above(c(" ", "Stage" = 3, "Module" = 7))
```

@@

To run the simulations we'll create a set of simulated candidates with an ability range between -4 and 4 (stepped in increments of 0.5). Then we'll repeat for each of the six designs above, using the same item bank.

@@

```{r}
kbl(head(displayParams, n = 1), caption = 'MST Design 1') %>%
  kable_styling() %>%
  add_header_above(c(" ", "Stage" = 3, "Module" = 7))
```

@@

kbl(head(dfTestResponses[1:8]), caption = 'Example Test Reponses') %>%
  kable_styling()
```

@@

kbl(dfCronbachsAlpha, caption = "Cronbach's Alpha") %>%
  kable_styling()

ggplot(dfCronbachsAlpha, 
       aes(x=alpha, y=num_responses, size = num_items, color = moduleNames)) +
    geom_point() +
    scale_x_continuous(limits = c(0, 1)) +
    theme(legend.position = "right") +
    labs(x = "alpha", y = "# responses") +
    geom_vline(xintercept = 0.7, linetype="dotted")
```

Ideally, we're looking for alphas of 0.7 and above; less than this indicates that there is weak covariance between the items in the module, which means they may not be testing the same trait. This measure is really only useful as a guide for further investigations; the ultimate decision on whether to modify the items in each module should be taken in collaboration with the subject matter experts.

@@

This chart makes it easy to spot any outlier items that have a very large divergence from the mean; it is best to remove these items from the item bank as they have too large an error (or rather too little information) to be used in a live test. Usually this is the result of them having all 1's or 0's (in other words they are too easy or too difficult for all candidates who took them).

@@

```{r Stage 1 MCC}
moduleA1_items <- which(colnames(dfTrial) %in% colnames(dfModuleAItems))
plotData <- trueScoreSummary(plot(raschmodel, 
                                  type = "ICC", 
                                  items = moduleA1_items, plot = FALSE), 
                             "A")
ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line() +
  labs(title="Module Characteristic Curve (Stage 1)", x="theta", y="True Score")
```

@@

ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curves (Stage 2)", x="theta", y="True Score")
```

@@

ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curves (Stage 3)", x="theta", y="True Score")
```
